Response to reviewers

### 2025-08-15 paper_plos/reviewer_respose_letter_V1.qmd
A few updates to draft response to reviewers.

Thank you for the kind words and for this helpful feedback. We've signfigicantly revised the manuscript, focusing on explaining things concisely and ensuring each paragraph is move forward the key points of each section. In summary:

- We've reduced the length of the manuscript from 34 to 28 pages (without references).
- We've removed tangential details and minimised the equations where possible, particularly in the “Early Research” section.
- We've streamlined the manuscript's text--to make each sections purpose more clear.
- We've removed redundancies where possible, especially in the "Family of Accessibility" section. 
- We've more clearly highlighted the paper's main contribution: namely, a review of the shared origins of spatial interaction modeling and accessibility, how their interpretations have diverged over time, and the introduction of a family of accessibility measures grounded in spatial interaction principles--including total, singly, and doubly constrained cases, as well as variants of “accessible opportunities” and “accessible population".

@@

Thannk you for your time and effort in reviewing our manuscript. We appreciate the constructive feedback and comments.

Thank you for this point. We agree, the inclusion of an empirical example would demonstrate the real-world applicability of the measures. However, due to the existing length of the document, the addition of an empirical example (even if we replaced the toy example) would still add additional length: we would need to add a condensed methods and data section, and dedicate more room for tests.

The length of the current document is an issue, so the addition of additional pages isn't feasible--especially given the concern over paper length that was raised by Reviewer 1 and how we’ve already reduced it by six pages in response to these concerns. However, we've put great thought into how the manuscript could be restructured to included an additional empirical example, but it just isn't possible given the manuscript's current format.

As such, we’ve clarified that the contribution of this work is primarily theoretical and methodological. We’ve also tempered earlier claims about the measure’s real-world applicability, instead allowing readers to consider potential uses and the potential value of reuniting accessibility measures with interpretable units. We plan to explore an empirical application in a future publication which make this contribution more practically clear--where we may have enough space to develop and explore an empirical example without shortchanging the historical context.

>>>>

Thank you for this point. We've significantly revised the manuscript, focusing on explaining things concisely and ensuring each paragraph is move forward the key points of each section. In summary:

- We've reduced the length of the manuscript from 34 to 28 pages (without references).
- We've removed tangential details and minimized the equations where possible, particularly in the “Early Research” section.
- We've streamlined the manuscript's text--to make each sections purpose more clear. The introductions and conclusions of sections now have a better flow.
- We've removed redundancies where possible, especially in the "Family of Accessibility" section. 
- We've more clearly highlighted the paper's main contribution: namely, a review of the shared origins of spatial interaction modeling and accessibility, how their interpretations have diverged over time, and the introduction of a family of accessibility measures grounded in spatial interaction principles--including total, singly, and doubly constrained cases, as well as variants of “accessible opportunities” and “accessible population".

The key points of the manuscript can be summarised as follows:
- First, it explicitly links accessibility to spatial interaction through their shared intellectual foundations (pre- @hansen1959), highlighting how contemporary accessibility research has diverged and showing the mathematical, intuitive, and interpretative advantages of preserving units through constrained formulations, as done in spatial interaction modeling.
- Second, it introduces 'constraints' to accessibility measures. First: the total constrained accessibility measure as an alternative to the Hansen-type formulation, producing zonal values that represent proportions of the known number of destination masses (i.e., opportunities) or origin masses (i.e., population) in the region. Second: the singly constrained accessibility measure as a competitive method that proportionally allocates opportunities from the destination based on population demand (from the origin), or in the case of market potential, proportional allocation of population from the origin based on the supply of opportunities at the destination. Its per-capita zonal rate is shown to be mathematically equivalent to the widely used two-step floating catchment area (2SFCA) method [@luo2003; @shen1998].

@@

Thank you for this point. We agree, the inclusion of an empirical example would demonstrate the real-world applicability of the measures. However, the length of the current document is an issue, so the addition of additional pages isn't feasible--especially given the concern over paper length that was raised by Reviewer 1 and how we’ve already reduced it by six pages in response to these concerns.

But, we've put great thought into how the manuscript could be restructured to included an additional empirical example. However, many of these ideas are not possible given the manuscript's current format. For instance, even if we replaced the toy example with an empirical example, it would still add quite significant additional length (i.e., explanation of data, room for tests). Further, a single empirical example is not sufficient to cover all cases and variants of the family.

As such, we’ve clarified that the contribution of this work: primarily theoretical and methodological. We’ve also tempered earlier claims about the measure’s real-world applicability, instead allowing readers to consider potential uses and the potential value of reuniting accessibility measures with interpretable units. While we believe these measures utility will be highlighted through real-world examples--we plan to explore these in future publications which make this contribution more practically clear (i.e., where we may have enough space to develop and explore an empirical example without shortchanging the historical context).
